Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
more texttt/textit tweaks

Similarly, while the Schema.org context
currently\footnote{\url{https://schema.org/version/13.0/schemaorg-current-http.jsonld}}
have \texttt{"@type": "@id"} annotations for object properties, RO-Crate
JSON-LD distinguishes explicitly between references to other entities
(\texttt{\{"@id": "\#alice"}\})
and string values (\texttt{"Alice"}) -- meaning
RO-Crate applications can find references for corresponding entities
and IRIs without parsing the \texttt{@context} to understand a particular
property. Notably this is exploited by the \texttt{ro-crate-html-js}
\cite{ro-crate-html-js} tool to provide reliable HTML rendering for
otherwise unknown properties and types.

>>>>

Similarly, while the Schema.org context
currently\footnote{\url{https://schema.org/version/13.0/schemaorg-current-http.jsonld}}
have \texttt{"@type": "@id"} annotations for implicit object properties, RO-Crate
JSON-LD distinguishes explicitly between references to other entities
\texttt{\{"@id": "\#alice"}\}
and string values \texttt{"Alice"} -- meaning
RO-Crate applications can find references for corresponding entities
and IRIs without parsing the \texttt{@context} to understand a particular
property. Notably this is exploited by the \textit{ro-crate-html-js}
\cite{ro-crate-html-js} tool to provide reliable HTML rendering for
otherwise unknown properties and types.
